%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%IEEE SPM template for Special Issue proposal  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%For this Latex template, font-size, line spacing, and margins are automatically adjusted as a function of the IEEEtran.cls class file. Nevertheless, there are some other points requiring your attention: White paper are not expected to cross the 5-page limit. In addition, up to 50 references are allowed (limit number for the final feature article), and excessive math should be avoided! 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[journal,onecolumn]{IEEEtran}
%%some useful packages.... you can add those you need...
\usepackage{graphics}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{fancybox}
\usepackage{amsmath}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{xcolor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{Special Issue Title}
\author{GEs with contact information }

% The paper headers
\markboth{Proposal for a Special Issue in IEEE SPM}%
{}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{About Special Issues}

{\color{blue} This section recall important issue concerning Special Issue (SI) Proposals. It must be removed when writing your white paper.}

A Special Issue (SI) comprises multiple, interrelated tutorials that provide a comprehensive coverage of a specific topic of interest to the signal processing community. Individuals interested in organizing a special issue as guest editors should submit a proposal to the Area Editor of Special Issues (refer to the Editorial page.) The proposal should include sufficient information and clear evidence addressing the following:
\begin{itemize}
        \item Motivation, timeliness, and importance of the topic (e.g., recent activities in conferences, research projects, and funding programs)
        \item Qualification, track records, and broad representation of the proposed guest editors (GEs). Include short bios of each proposing GE
        \item A tentative list of topics covered in the special issue
        \item A tentative schedule of submission and review
        \item Relation to any recent special issues published or planned for publication in SPM or other journals/transactions/magazines
        \item References
       
\end{itemize}

 Proposers are encouraged to include a team of GEs with a broad representation from different organizations and countries. Proposals with overlap with any topic covered recently or in the near future in Signal Processing Magazine (SPM) or other publications are discouraged. The list of recent topics covered by SPM is available on the SPS website Special Issues page.
 
{\color{blue} The content of a Special Issue proposal is detailled below. Please, remove this section, and fill in the sections below following the short instructions (that have also to be removed), and then submit your SI proposal in ScholarOne.}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Scope}
\par One paragraph describing the main topic of the special issue. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation, timeliness, and importance of the topic }
\label{secrel}
\par Explain why the topic is relevant, important and timely for the Signal Processing Society (SPS) community such that a special issue on the topic is justified.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Guest editors (GEs)}
\label{secge}
\par Describe the qualification, track records, and broad representation of the proposed guest editors (GEs). Include short bios of each proposing GE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A tentative list of topics}
\label{secge}
\par Describe a tentative list of topics to be covered by the special issue
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A tentative list of potential authors}
\label{secge}
\par Describe a tentative list of potential authors, that you could invite for contributing to the SI

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A draft of the call for papers (CFP) including a tentative schedule of submission and review}
\label{secge}
\par Prepare a 1-page draft of the CFP, including the agenda of the special issue steps following the timing of the example. Note that SPM issues are published every 2 months, and that the final files must be ready at least 3 months before publication.
\begin{enumerate}
    \item 8/1/18 White paper due
    \item 9/1/18 Invitation notification
    \item 11/1/18 Full length manuscripts due
    \item 1/1/19 First review to authors
    \item 3/1/19 Revision due
    \item 5/1/19 Final decision
    \item 6/1/19 Final package due
    \item 9/1/19 Publish manuscript
\end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relation to any recent SPS special issues}
\label{secge}
\par Describe the relation of the proposed special issue to any recent special issues published or planned for publication in SPM or other journals/transactions/magazines of SPS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{references}
\label{secref}
\par Please list no more than 20 most relevant references. self-citation shall be limited.
%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}





