%!TEX root = ../thesis.tex
% Acknowledgments
    \newpage
    \pdfbookmark[0]{Acknowledgments}{acknowledgments}
    \chapter*{Acknowledgments}
This thesis describes my research which was conducted from February 2021 to October 2022 during my MS Studies at Pakistan Navy Engineering College, a constituent college of the National University of Science Technology (NUST) at its campus at Karachi.
    \par
I am really grateful to Almighty Allah for giving me the consistency, fortitude, guidance, wisdom, and strength to successfully accomplish my task regarding making a successful ASR to detect malicious sentences. This thesis report has been written to fulfill the requirement of MS Degree Program.
    \par 
I am truly honored that Pakistan Navy selected me to undergo MS at PNEC. I am grateful to my advisor, Professor Dr. Arshad Aziz, whose support, supervision, and encouragement from the initial to the final stage enabled me to carry out the complete project successfully. My special thanks to the GEC committee members Cdre Dr. Nazeer A. Malik and Dr. Bilal M. Khan.
    \par
I am also truly grateful to Citizen Police Liaison Committee, especially Mr. Zubair (Chief CPLC), Mr. Ali Haji and Mr. Raheem Ali for providing PNEC-NUST providing resources to help bring this project to life. I am also grateful to the Kaldi Open Source Community who have guided me in the practical implementation of this work.  
    \par
Lastly I put forward my consent and regards to my wife and my son who are the source of my motivation for everything. I would like to acknowledge the support from my sisters Sanila, Ayela, and Mareeha. My family has been my support system and I would also like to acknowledge the support of Jawad, Nashwa, Zaki, and Nehal. Finally, I thank my Parents who have always provided me with the best possible resources to complete this work.